---
title: "Exploring titanic dataset in R"
output: html_notebook
---
## Variable definitions
from https://www.kaggle.com/c/titanic/data

| Variable	| Definition	| Key
| --- | --- | --- |
| survival	| Survival	| 0 = No, 1 = Yes|
| pclass	| Ticket class	| 1 = 1st, 2 = 2nd, 3 = 3rd|
| sex	| Sex	| |
|Age	| Age in years	| |
|sibsp	|# of siblings / spouses aboard the Titanic	| |
|parch	|# of parents / children aboard the Titanic	| |
|ticket	|Ticket number	| |
|fare	|Passenger fare	| |
|cabin	|Cabin number	| |
|embarked |	Port of Embarkation |	C = Cherbourg, Q = Queenstown, S = Southampton|

```{r installing libraries, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggExtra)
library(ggthemes)
library(scales)
library(dplyr)

theme_set(theme_clean())
```

```{r read dataset, message=FALSE, warning=FALSE}
train <- read.csv('train.csv')
test <- read.csv('test.csv')

combined <- bind_rows(train, test)
```

```{r}
colnames(train)
```

```{r}
summary(train)
```
Seems like Age has a bunch of missing values :/ We can impute them later.

*TODO*: Impute age from other variables;

Assuming that older folks, kids and women were prioritized for lifeboats and had a higher chance of survival. Let's see if this is true.

### Compute group survival rates by some categorical vars:
  - sex
  - age group
  - passenger class

Instead of looking at age (which is continuous variable), we should look at range of age i:e bin it.

So we will create a new variable called AgeBin which will contain age range.
```{r}
train$AgeBin = cut(train$Age, breaks = c(seq(10, 100, 10)))
```
Let's look at the survival rate distribution now.

Dropping NA values for now and sorting groups by survival rate.
```{r}
survival <- train %>% select(AgeBin, Sex, Pclass, Survived) %>% group_by(AgeBin, Sex, Pclass) %>% summarise(Mean = mean(Survived)) %>% filter(!is.na(AgeBin)) %>% arrange(desc(Mean))

survival
```